error checking the LE decomp functions

### 2016-10-25 Code/error checking the LE decomp fxs.Rmd
fixed error in cod decomp fx

Our functions:
```{r source_LE_fxs}
library(dplyr)
library(ggplot2)
source("/Users/corinneriddell/Documents/repos/BlackWhiteGap/Code/life_expectancy_functions.R")
```

@@

We also need data on the proportion of deaths within each age bracket due to each cause of death.
```{r data_cod_proportions}
cod.props <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteGap/working_teaching_examples/auger_cod_proportions.csv")
names(cod.props)[3] <- "prop.QC"
names(cod.props)[4] <- "prop.CAD"
head(cod.props)
```

Calculate and display the life tables for the Canada and Quebec data:
```{r calculate_life_expectancy}
life.table.cm <- life.table(data = canada.men, age.groups = "ages", num.ages.in.group = "n_x", 
                            death.counts = "obs.deaths", population.counts = "obs.popn")

@@

life.table.qm <- life.table(data = quebec.men, age.groups = "ages", num.ages.in.group = "n_x", 
                            death.counts = "obs.deaths", population.counts = "obs.popn")

@@

```{r calc_age_decomp}
age_decomp <- le_age_decomp(life.table1 = life.table.qm, name.lt1 = "Quebec", 
                            life.table.cm, name.lt2 = "Canada", 
                            age.groups = "ages")
age_decomp
sum(age_decomp$C_x) 
```

>>>>

Our functions:
```{r source_LE_fxs}
library(dplyr)
library(ggplot2)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

@@

We also need data on the proportion of deaths within each age bracket due to each cause of death.
```{r data_cod_proportions}
cod.props <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/working_teaching_examples/auger_cod_proportions.csv")
names(cod.props)[3] <- "prop.QC"
names(cod.props)[4] <- "prop.CAD"
head(cod.props)
```

Calculate and display the life tables for the Canada and Quebec data:
```{r calculate_life_expectancy}
life.table.cm <- life.table(data = canada.men, num.ages.in.group = "n_x", 
                            death.counts = "obs.deaths", population.counts = "obs.popn")

@@

life.table.qm <- life.table(data = quebec.men, num.ages.in.group = "n_x", 
                            death.counts = "obs.deaths", population.counts = "obs.popn")

@@

```{r calc_age_decomp}
age_decomp <- le_age_decomp(life.table1 = life.table.qm, name.lt1 = "Quebec", 
                            life.table2 = life.table.cm, name.lt2 = "Canada", 
                            age.groups = "ages")
age_decomp
sum(age_decomp$C_x) 
```
